---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RGremlinsConjoint

<!-- badges: start -->
<!-- badges: end -->

The gremlins package provides the tools and utilities to estimate a the model described in
  "Gremlin's in the Data: Identifying the Information Content of Research Subjects" using
  conjoint analysis data such as that collected in Sawtooth Software's Lighthouse or Discover
  Products.  The packages also contains utility functions for formatting the input data and
  extracting the relevant results.

## Installation

<!-- You can install the released version of RGremlinsConjoint from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("RGremlinsConjoint") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("statuser/RGremlinsConjoint")
```
## Example

The package exposes basically one function  You can use it like:

```{r example}
library(RGremlinsConjoint)

# Read in the data
truck_design_file <- system.file("extdata", "simTruckDesign.csv", package = "RGremlinsConjoint")
truck_data_file <- system.file("extdata", "simTruckData.csv", package = "RGremlinsConjoint")
truckDesign <- read.csv(truck_design_file)
truckData <- read.csv(truck_data_file)

# Covert the design file to be dummy coded is necessary
# The simulated data is already coded
# codedTruck <- code_sawtooth_design(truckDesign, c(4:9), include_none_option=TRUE)

outputSimData_burn <- estimateGremlinsModel(truckData,
                                            truckDesign,
                                            R = 100000,
                                            keepEvery = 1,
                                            num_lambda_segments = 2)

```

